Preparing for Potential Closure of European Airspaces due to Reentering Space Objects

### 2025-04-30 paper.qmd
sort of final structure draft

```{r collision}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("media/figures/cubes.png")
```

@@

In few days (at the time of writing this paper) around May 10, 2025, the
KOSMOS 482 Descent Craft should reenter the Earth atmosphere [@kosmos482reentry].
This is supposedly the lander module from a 1972 failed Soviet Venera mission
[@SpaceReviewKosmos] of \qty{480}{kg} weight and circa \qty{1}{m} diameter.
Being supposed to survive Venus's atmosphere which is much denser and hotter than Earth's atmosphere (surface pressure 93 times that of Earth and temperatures reaching \qty{467}{degreesCelsius} (\qty{872}{degreesFarenheit})).
So it could re-enter Earth intact and not break into smaller fragments some of which could burn up.

@@

# Conclusion / Outcome

@@

# Appendix {.appendix}

## Orbital Elements {#sec-orbitals .appendix}
We refer to @fig-orbital-elements to describe the orbital parameters of
interest for the current work.

:::{#fig-orbital-elements layout="[40,-3,57]" fig-env="figure*"}

![Keplerian elements: semi-major axis, $a$, the eccentricity, $e = \frac{2c}{2a}$. (the semiparameter (a.k.a. _semilatus rectum_), $p$, describes the size of the conic section by defining the width at the primary focus, and is defined as
$p = b^2 / a = a (1 - e^2)$)](media/figures/classical_orbital_elements_2.png)

![Keplerian elements: inclination, $i$, the right ascension of the ascending node, $\Omega$ , and the argument of periapsis, $\omega$.(Earth rotates around $\hat{K}$)](media/figures/classical_orbital_elements_4.png)

@@

@@

>>>>

```{r collision}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("media/example-image.png")
```

@@

In few days (at the time of writing this paper) at 6h May 10, 2025
($\pm 2.8$ days), the KOSMOS 482 Descent Craft should reenter the
Earth's atmosphere [@kosmos482reentry].
This is supposedly the lander module from a 1972 failed Soviet Venera mission
[@SpaceReviewKosmos] of \qty{480}{kg} weight and circa \qty{1}{m} diameter.
Being supposed to survive Venus's atmosphere which is much denser and hotter than Earth's atmosphere (surface pressure 93 times that of Earth and temperatures reaching \qty{467}{degreesCelsius} (\qty{872}{degreesFarenheit})).
So it could re-enter Earth intact and not break into smaller fragments some of which could burn up.

With what developed in this paper, we can derive the casuality risk and
determine the maximum value using data for the busiest day in 
the busiest 2024 week.

Once the reentry track is known more or less accurately, the relevant
H3 cells can be

::: {#fig-kosmos}

```{r kosmos}
#| out-width: "100%"
#| echo: false
knitr::include_graphics("media/example-image.png")
```

Casuality for KOSMOS 482 Descent Craft reentry. 
:::

@@

# Conclusion and Future work

@@

Future work will explore the impact of megacostellations and the risk for
European airspace.

# Appendix {.appendix}
# Orbital Elements {#sec-orbitals }

:::{#fig-orbital-elements layout="[40,-4,56]" fig-env="figure*" fig-pos="t"}

```{r ellipse-parameters}
#| fig-cap: "Keplerian elements: semi-major axis, $a$, the distance between the foci, $2c$, the eccentricity, $e = (2c)/(2a)$. (the semiparameter (a.k.a. _semilatus rectum_), $p$, describes the size of the conic section by defining the width at the primary focus, and is defined as $p = b^2 / a = a (1 - e^2)$)"

#| echo: false
knitr::include_graphics("media/figures/classical_orbital_elements_2.png")
```

```{r keplerian-elements}
#| fig-cap: "Keplerian elements: inclination, $i$, the right ascension of the ascending node, $\\Omega$ , and the argument of periapsis, $\\omega$.(Earth rotates around $\\hat{K}$)"
#| echo: false

knitr::include_graphics("media/figures/classical_orbital_elements_4.png")
```

@@

We refer to @fig-orbital-elements to describe the orbital parameters of
interest for the current work.

@@

These are used to derive numerically compute the weighting function,
@fig-weighting-inclination-i:
for debris with inclination $i$ we simulate an orbit of $N$, i.e. $10001$,
positions and calculate the corresponding cartesian position and the
equivalent longitude and latitude.
